\vbox to \myposterheight{%

%----------------------------------------------------------------------------------------
%	DECONVOLUTION
%----------------------------------------------------------------------------------------
\begin{block}{Deconvolution of ultrasound images}
	\begin{itemize}
		\item The proposed model relates the low-resolution RF image with the high-resolution TRF 
		\item It can be used for \textbf{deconvolution} \textit{i.e.} to retrieve the TRF from the DAS image 
		\item Let us define the RF image $\vect{s} \in \mathbb{R}^{N_{\Omega}}$ and the unknown TRF $\vect{\gamma} \in \mathbb{R}^{N_{\Omega}}$ over the spatial grid $\Omega = \left\lbrace \ser{\vect{r}}{j}, j = 1, \dots, N_{\Omega}\right\rbrace$
		\item The estimate of the TRF can be expressed from the RF image as:
		\begin{equation*}
			\vect{\gamma} \in \arg \min \limits_{\hat{\vect{\gamma}} \in \mathbb{R}^{N_{\Omega}}} \| \hat{\vect{\gamma}} \|_p \textnormal{ subject to } \| \mat{H} \hat{\vect{\gamma}} - \vect{s} \| \leq \epsilon
		\end{equation*}
		where $p \in \left]0, 2\right]$ and $\mat{H} \in \mathbb{R}^{N_{\Omega} \times N_{\Omega}}$ is defined by:
		\begin{equation*}
			H_{jk} = PSF \left(\ser{\vect{r}}{j}, \ser{\vect{r}}{k}\right), \; \forall \left(\ser{\vect{r}}{j}, \ser{\vect{r}}{k}\right) \in \Omega^2 
		\end{equation*}
	\end{itemize}
\end{block}

%----------------------------------------------------------------------------------------
%	EXPERIMENTS AND RESULTS
%----------------------------------------------------------------------------------------

\begin{block}{Experiments and results}
	\begin{itemize}
		\item Comparison with state-of-the-art deconvolution approaches which use spatially-invariant PSF~\cite{Chen2015}
		\item Raw-data simulated on Field II:
		\begin{itemize}
			\item 64-elements phased-array
			\item Central frequency $f_c$ = \SI{2.5}{\mega\hertz}, bandwidth of \SI{80}{\percent} 
			\item Sampling frequency $f_s$ = 
		\end{itemize}
		\item Standard DAS algorithm used to obtain the RF image
	\end{itemize}
\end{block}
\vfill

%----------------------------------------------------------------------------------------
%	CONCLUSION
%----------------------------------------------------------------------------------------

\begin{block}{Conclusion}
	
\end{block}
\vfill

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\begin{block}{References}
	\printbibliography
\end{block}
\vfill
%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\begin{block}{Acknowledgments}
	
	\begin{itemize}
		\item Nam mollis tristique neque eu luctus. Suspendisse rutrum congue nisi sed convallis. Aenean id neque dolor. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
		\item Nam mollis tristique neque eu luctus. Suspendisse rutrum congue nisi sed convallis. Aenean id neque dolor. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
	\end{itemize}
	
\end{block}
}